---
title: "Bible Study Tool"
subtitle: "ASV with Strong’s (Enhanced)"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    number_sections: false
    code_folding: hide
    df_print: paged
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  out.width = "100%",
  fig.retina = 2
)
```

```{r packages}
suppressPackageStartupMessages({
  library(tidyverse)
  library(DT)
  library(jsonlite)
  library(purrr)
  library(tidyr)
  library(stringr)
  library(glue)
  library(htmltools)
  library(htmlwidgets)
})
```

<!-- Meta, favicon, and Google Fonts -->
```{r meta, results='asis'}
cat('
<meta name="viewport" content="width=device-width, initial-scale=1" />
<link rel="icon" href="data:image/svg+xml,%3Csvg xmlns=%27http://www.w3.org/2000/svg%27 viewBox=%270 0 100 100%27%3E%3Ctext y=%27.9em%27 font-size=%2790%27%3E📖%3C/text%3E%3C/svg%3E">
<link href="https://fonts.googleapis.com/css2?family=Inter:wght@400;600;700&family=Playfair+Display:wght@600;700&family=JetBrains+Mono:wght@400;600&display=swap" rel="stylesheet">
')
```

<!-- Page styles (kept inline so the HTML is portable) -->
```{r styles, results='asis'}
css <- '
:root {
  --hero-bg: radial-gradient(1200px 600px at 10% 0%, #efeaff 0%, #ffffff 60%);
}
body {
  line-height: 1.6;
  font-family: Inter, system-ui, -apple-system, Segoe UI, Roboto, Ubuntu, Cantarell, "Helvetica Neue", Arial, "Noto Sans", "Apple Color Emoji", "Segoe UI Emoji";
}
h1, h2, h3, .h1, .h2, .h3 {
  font-family: "Playfair Display", Georgia, "Times New Roman", Times, serif;
}
pre, code, kbd, samp { font-family: "JetBrains Mono", ui-monospace, SFMono-Regular, Menlo, Monaco, Consolas, "Liberation Mono", "Courier New", monospace; }
.hero {
  background: var(--hero-bg);
  border-radius: 1.25rem;
  padding: 2.25rem 1.5rem;
  margin-bottom: 1.25rem;
  border: 1px solid rgba(111,78,242,0.12);
}
.hero h1, .hero h2, .hero h3 {
  margin: 0 0 .35rem 0;
}
.hero p.lead {
  font-size: 1.05rem;
  margin: .25rem 0 0 0;
  color: #444;
}
.metrics {
  display: grid;
  grid-template-columns: repeat(auto-fit, minmax(180px, 1fr));
  gap: .75rem;
  margin-top: 1rem;
}
.metric {
  background: #fff;
  border: 1px solid rgba(0,0,0,.06);
  border-radius: 1rem;
  padding: .9rem 1rem;
  box-shadow: 0 6px 20px rgba(0,0,0,.04);
}
.metric h4 {
  font-weight: 700; margin: 0; font-size: 1.35rem;
}
.metric small { color:#666 }
.tag {
  display:inline-block; padding:.18rem .55rem; margin:.12rem .25rem .12rem 0;
  font-size:.84rem; border-radius:999px; border:1px solid rgba(111,78,242,.25);
  background:rgba(111,78,242,.06); color:#2b1b80; text-decoration:none;
}
.tag:hover { background:rgba(111,78,242,.12); border-color:rgba(111,78,242,.5) }
blockquote {
  background: #f9fafc; border-left: 4px solid #6f4ef2; padding: .8rem 1rem; border-radius:.5rem;
}
.section-note {
  background: #f7fbff; border:1px solid rgba(31,155,207,.2); border-radius: .9rem; padding: 1rem 1.1rem;
}
hr.faint { border: none; border-top:1px dashed rgba(0,0,0,.12); margin: 1.5rem 0; }

/* DataTables polish */
.dataTables_wrapper .dt-buttons .btn { border-radius: 999px; }
table.dataTable tbody tr { line-height: 1.25rem; }
table.dataTable thead th, table.dataTable thead td { border-bottom: 1px solid rgba(0,0,0,.1); }
div.dtsp-panel { border-radius: .75rem !important; }
.dtsp-searchPane { border-radius: .75rem !important; }
.fixedHeader-floating { border-radius: .6rem; }

/* Floating back-to-top */
#backToTop {
  position: fixed; right: 18px; bottom: 18px; display: none; z-index: 9999;
  border: none; border-radius: 999px; padding: .6rem .8rem; font-weight:600;
  background: #6f4ef2; color: #fff; box-shadow: 0 6px 18px rgba(111,78,242,.35);
}
#backToTop:hover { filter: brightness(1.05); }
'
htmltools::tags$style(HTML(css))
```

## Overview

<div class="hero">
  <h1 class="display-6">Bible Study Tool</h1>
  <p class="lead">Explore the ASV text with Strong’s numbers and enhanced glosses. Filter by book, chapter, or Strong’s code, and export selections for deeper study.</p>
  <div class="metrics">
    <div class="metric">
      <h4 id="m-verses">—</h4>
      <small>Total verses</small>
    </div>
    <div class="metric">
      <h4 id="m-books">—</h4>
      <small>Books</small>
    </div>
    <div class="metric">
      <h4 id="m-unique">—</h4>
      <small>Unique Strong’s codes</small>
    </div>
    <div class="metric">
      <h4 id="m-avg">—</h4>
      <small>Avg. codes / verse</small>
    </div>
  </div>
</div>

> Tip: you can pre-filter via URL. For example, append `?q=H430` to search for a specific Strong’s code.

---

## Load data

```{r data}
# Read your CSV
asvs_strongs_enhanced <- readr::read_csv(
  "asvs_strongs_enhanced.csv",
  show_col_types = FALSE
)

# Helper: parse the Python-like list strings into proper R lists
parse_list <- function(x) {
  if (is.na(x) || !nzchar(x)) return(list(character()))
  # Replace single quotes with double, ensure JSON compatibility
  x <- gsub("'", '"', x, fixed = TRUE)
  out <- tryCatch(jsonlite::fromJSON(x), error = function(e) character())
  as.list(out)
}

# Build verse reference and linkable Strong's tags
display_df <- asvs_strongs_enhanced %>%
  mutate(
    verse_ref = glue("{book_name} {chapter}:{verse}"),
    strongs_list = map(strongs, parse_list),
    defs_list    = map(strongs_enhanced, parse_list),
    strongs_tags = map_chr(strongs_list, ~{
      codes <- .x %>% unlist()
      if (length(codes) == 0) return("")
      paste0(
        vapply(
          codes,
          function(code) glue('<a class="tag" href="https://www.blueletterbible.org/lexicon/{tolower(code)}/kjv/wlc/0-1/" target="_blank" rel="noopener">{code}</a>'),
          FUN.VALUE = character(1)
        ),
        collapse = " "
      )
    })
  ) %>%
  select(
    Book = book_name,
    Chapter = chapter,
    Verse = verse,
    Reference = verse_ref,
    `Plain Text` = plain_text,
    `Enhanced (with glosses)` = text_enhanced,
    `Strong\'s Count` = strongs_count,
    `Strong\'s` = strongs_tags,
    strongs_list, defs_list   # keep for later index build (hidden)
  )

# Quick stats for hero metrics
n_verses <- nrow(display_df)
n_books  <- n_distinct(display_df$Book)

# Unique Strong's across the corpus
all_codes <- display_df$strongs_list %>%
  flatten_chr() %>%
  unique()
n_unique <- length(all_codes)

avg_codes <- mean(asvs_strongs_enhanced$strongs_count, na.rm = TRUE) %>% round(2)
```

```{r metrics-js, results='asis'}
htmltools::tags$script(HTML(glue("
document.addEventListener('DOMContentLoaded', function(){{
  document.getElementById('m-verses').textContent = '{format(n_verses, big.mark=",")}';
  document.getElementById('m-books').textContent = '{n_books}';
  document.getElementById('m-unique').textContent = '{format(n_unique, big.mark=",")}';
  document.getElementById('m-avg').textContent = '{avg_codes}';
}});
")))
```

## Read & filter verses

```{r verses-table}
# Build the main interactive table
DT::datatable(
  display_df %>% select(Book, Chapter, Verse, Reference, `Plain Text`, `Enhanced (with glosses)`, `Strong\'s Count`, `Strong\'s`),
  rownames = FALSE,
  escape = FALSE, # allow HTML tags for Strong's chips
  filter = "top",
  options = list(
    deferRender = TRUE,
    scrollY = 600,
    scroller = TRUE,
    fixedHeader = TRUE,
    dom = "PBfrtip",
    pageLength = 25,
    lengthMenu = list(c(10, 25, 50, 100, -1), c("10", "25", "50", "100", "All")),
    buttons = list(
      list(extend = "copy", title = "Bible Study Tool"),
      list(extend = "csv", title = "bible_study_tool"),
      list(extend = "excel", title = "bible_study_tool"),
      list(extend = "pdf", title = "bible_study_tool", orientation = "landscape", pageSize = "A4"),
      list(extend = "print", title = "Bible Study Tool")
    ),
    extensions = c("Buttons", "FixedHeader", "Scroller", "ColReorder", "SearchPanes"),
    searchPanes = list(
      cascadePanes = TRUE,
      viewTotal = TRUE,
      layout = "columns-3",
      # Enable panes for Book and Chapter; others through global search
      columns = c(0, 1)
    ),
    columnDefs = list(
      list(searchPanes = list(show = TRUE), targets = c(0,1)),
      list(orderable = FALSE, targets = 7) # Strong's chips column not sortable
    )
  ),
  elementId = "verses_table",
  class = "stripe hover row-border order-column"
) %>%
  # Prefill search from URL param ?q= (works for Strong's code, book, etc.)
  DT::formatStyle(0, target = "row") %>%
  htmlwidgets::onRender("
    function(el, x) {
      const params = new URLSearchParams(window.location.search);
      const q = params.get('q');
      if (q) {
        const tbl = $(el).DataTable();
        tbl.search(q).draw();
      }
      // Placeholder text for global search input
      setTimeout(function(){
        const wrapper = $(el).closest('.dataTables_wrapper')[0];
        if(!wrapper) return;
        const search = wrapper.querySelector('input[type=search]');
        if (search) search.placeholder = 'Search by text, book, or Strong\\'s code (e.g., H430)…';
      }, 0);
    }
  ")
```

---

## Strong’s Index (auto-generated)

This index is derived from the CSV on the fly—counts each Strong’s code across all verses and shows the most common first. Click a code to jump to an external lexicon entry.

```{r strongs-index}
# Build a long table of codes with their (first-found) gloss text
index_df <- display_df %>%
  mutate(row_id = row_number()) %>%
  mutate(
    code_def_pairs = pmap(
      list(strongs_list, defs_list),
      function(codes, defs) {
        codes <- unlist(codes); defs <- unlist(defs)
        if (length(codes) == 0) return(tibble(code = character(), def = character()))
        # align length differences conservatively
        n <- min(length(codes), length(defs))
        tibble(code = codes[seq_len(n)], def = defs[seq_len(n)])
      }
    )
  ) %>%
  select(row_id, Book, Chapter, Verse, code_def_pairs) %>%
  unnest(code_def_pairs) %>%
  group_by(code) %>%
  summarize(
    Occurrences = n(),
    Example = first(glue("{Book} {Chapter}:{Verse}")),
    Definition = first(def),
    .groups = "drop"
  ) %>%
  arrange(desc(Occurrences)) %>%
  mutate(
    `Strong\'s` = glue('<a class=\"tag\" href=\"https://www.blueletterbible.org/lexicon/{tolower(code)}/kjv/wlc/0-1/\" target=\"_blank\" rel=\"noopener\">{code}</a>')
  ) %>%
  select(`Strong\'s`, Occurrences, Example, Definition)

DT::datatable(
  index_df,
  rownames = FALSE,
  escape = FALSE,
  filter = "top",
  options = list(
    pageLength = 25,
    dom = "Bfrtip",
    buttons = list(
      list(extend = "copy", title = "strongs_index"),
      list(extend = "csv", title = "strongs_index"),
      list(extend = "excel", title = "strongs_index")
    ),
    order = list(list(1, "desc"))
  ),
  elementId = "strongs_index",
  class = "stripe hover row-border"
)
```

---

## Notes

<div class="section-note">
  <ul>
    <li><strong>Export:</strong> Use the buttons above each table to copy or download your filtered results.</li>
    <li><strong>Deep links:</strong> Add <code>?q=H7225</code> (or any text) to the URL to pre-search the verses table.</li>
    <li><strong>Attribution:</strong> Scripture is ASV; Strong’s numbers &amp; glosses derived from your CSV.</li>
  </ul>
</div>

```{r back-to-top, results='asis'}
htmltools::tags$button(id="backToTop", "Top")
```

```{r back-to-top-script, results='asis'}
htmltools::tags$script(HTML("
  const btn = document.getElementById('backToTop');
  window.addEventListener('scroll', () => {
    if (window.scrollY > 400) { btn.style.display = 'block'; }
    else { btn.style.display = 'none'; }
  });
  btn.addEventListener('click', () => window.scrollTo({top:0, behavior:'smooth'}));
"))
```

---

### How to publish this as a web page (GitHub Pages)

1. Save this file as `index.Rmd` in your repo (keep the CSV path the same).
2. Knit to HTML in RStudio: **Knit ▶ index.html**.
3. Commit and push the generated `index.html` plus any referenced assets.
4. In your GitHub repo: **Settings ▶ Pages ▶ Build and deployment ▶ Source = Deploy from a branch**.
   - Choose the branch (e.g., `main`) and folder (root if `index.html` is in root, or `docs` if you prefer that).
5. Save. Your site will appear at `https://<username>.github.io/<repo>/`.
